Pre-Trained Denoising Autoencoders Long Short-Term Memory Networks as probabilistic Models for Estimation of Distribution Genetic Programming

### 2023-01-11 slides.Rmd
autogit

```{r airfoil_fullRun_2hl_maxIndSize_params, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}
fig.pos="H"
knitr::kable(
  read.csv("./tables/airfoil_fullRun_2hl_maxIndSize_params"),
  caption="Hyperparameter"
)%>% row_spec(0,bold=TRUE ) %>% kableExtra::kable_styling(latex_options = "hold_position")
```
## Funktions Set Symbolische Regression

```{r airfoil_function_set, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}
fig.pos="H"
knitr::kable(
  read.csv("./tables/airfoil_function_set"),
  #caption="Funktions Set"
)%>% row_spec(0,bold=TRUE ) %>% kableExtra::kable_styling(latex_options = "hold_position")
```

>>>>

```{r airfoil_fullRun_2hl_maxIndSize_params, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}
fig.pos="H"
knitr::kable(
  read.csv("./tables/airfoil_fullRun_2hl_maxIndSize_params"),
  # caption="Hyperparameter"
)%>% row_spec(0,bold=TRUE ) %>% kableExtra::kable_styling(latex_options = "hold_position")
```
## Funktions Set Symbolische Regression

```{r airfoil_function_set, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}
fig.pos="H"
knitr::kable(
  read.csv("./tables/airfoil_function_set"),
  # caption="Funktions Set"
)%>% row_spec(0,bold=TRUE ) %>% kableExtra::kable_styling(latex_options = "hold_position")
```
